% !TEX root = dissertation_BB.tex
%% spellcheck-language en-US

\cleardoublepage
\chapter*{Acknowledgements}
\markboth{\MakeUppercase{Acknowledgements}}{}
\addcontentsline{toc}{chapter}{Acknowledgements}

The work presented in this thesis has been carried out in the Hufnagel group at the European Molecular Biology Laboratory (EMBL) in Heidelberg, Germany. I would like to thank Lars Hufnagel for this unique opportunity to work in the field of microscopy, and for his continuous support through the project.
\\[1ex]
I am very grateful to the members of my thesis advisory committee: Jonas Ries, Takashi Hiiragi and Balázs Rózsa; thank you for the support and the fruitful discussions.
\\[1ex]
I would also like to thank Prof. Péter Szolgay for the opportunity to be part of the Roska Tamás Doctoral School of Sciences and Technology at Pázmány Péter Catholic University.
\\[1ex]
I would like to thank Gustavo Quintas Glasner de Medeiros and Nils Norlin for the microscope building and debugging sessions, and for sharing all their experience and knowledge.
A big thank you to Marvin Albert and Joran Deschamps for their help with the compression algorithm, and also for sharing the ups and downs of EMBL PhD life.
\\[1ex]
Many thanks to all friends and colleagues who helped me throughout my four years: 
Dimitri Kromm,
Ulla-Maj Fiuza,
Li-Ling Yang,
Stefan Günther,
Lucía Durrieu,
Patrick Hoyer,
Laura Panavaite,
Uroš Kržič,
Petr Strnad,
Sebastian Streichan,
Aldona Nowicka,
Christina Besir,
Tatjana Schneidt,
Judith Reichmann,
Yu Lin,
Nils Florian Wagner,
Christian Tischer;
% José Quintero;
it has been a truly memorable time.
\\[1ex]
Development of the microscope would not have been possible without the expert help of Alfons Riedinger, Alejandro Gil Ortiz, Leo Burger, Sascha Blättel, Tim Hettinger and all other members of the EMBL electronic and mechanical workshops.
\\[1ex]
Special thanks goes to Judit Tóth, István Gärtner and Attila Mócsai for introducing me to the world of natural sciences, and Prof. Szabad János for showing me EMBL for the first time.
\\[1ex]
I am eternally grateful to my parents and my first scientific advisors, Béla Balázs and Ilona Fige, and my sister, Eszter for their unconditional support.
\\[1em]
Finally, Melánia: Thank you for your infinite patience, support and love.