\section{New scientific results}

\paragraph{Thesis I.}\textit{I have designed and constructed a new light-sheet microscope suitable for high sensitivity imaging of delicate samples. A novel  arrangement of two high numerical aperture objectives in 120 degrees allows for near isotropic resolution while increasing light collection efficiency by a factor of two.}\\[0.5ex]
Corresponding publications: \cite{de_medeiros_light-sheet_2016},\cite{strnad_inverted_2016}, \cite{hoyer_breaking_2016}\\[0.5ex]
Live imaging of light sensitive specimens, such as a developing mouse embryo is a challenging task

\paragraph{Thesis II.} \textit{I have developed a GPU-based image procesing pipeline for multi-view light-sheet microscopy that enables real time fusion of opposing views.}

Corresponding publications: \cite{balazs_gpu-based_2016}, \cite{balazs_gpu-based_2016-1}, \cite{balazs_gpu-based_2017}



\paragraph{Thesis III.} \textit{I have  developed a new image compression algorithm that enables noise dependent lossy compression of light microscopy images, and can reach a compression ratio of 100 fold while preserving the results of downstream data analysis steps.}

Corresponding publications: \cite{balazs_real-time_2017}, \cite{balazs_gpu-based_2016}, \cite{balazs_gpu-based_2016-1}, \cite{balazs_gpu-based_2017}\\[1ex]
\indent
All microscopy images contain inherent noise, that is 


\paragraph{Thesis IV.} \textit{I have  developed a new GPU-based image compression library, \b3d, that implements the algorithm described in Thesis III, and allows for real time compression of microscopy images with a throughput of up to 1 GB/s.}\\[0.5ex]
Corresponding publications: \cite{balazs_real-time_2017}, \cite{balazs_gpu-based_2016}, \cite{balazs_gpu-based_2016-1}, \cite{balazs_gpu-based_2017}\\[0.5ex]
\b3d is an efficient, GPU-based image compression library allowing lossless and noise dependent lossy compression of microscopy images. Since many high-speed microscopy methods generate immense amounts of data, easily reaching terabytes per experiment, image compression is especially important to efficiently deal with such datasets.